Overview of the eHealth Knowledge Discovery Challenge at IberLEF 2021

### 2021-06-28 paper/paper.tex
Add transfer

\documentclass[a4paper,11pt,twocolumn,twoside]{article}
\usepackage{graphicx}
\usepackage{sepln_en}
\usepackage{fullname}
\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{todonotes}
% \usepackage[spanish,es-nosectiondot, es-tabla, es-noindentfirst, es-nolists]{babel}

@@

\seplnabstract{This paper summarises the eHealth Knowledge Discovery Challenge hosted at IberLEF 2021. The task, resources, and participating systems are described. The main results are highlighted and discussed. The best performing systems are analysed, and recommendation for future research are presented.}

@@

The Challenge is based on a corpus of documents composed of
sentences taken from previous challenges and other resources,
and newly annotated sentences.
The corpus is divided into three collections: training, development, and testing.
All collections contain sentences extracted from MedlinePlus, Wikinews, and the CORD-19 corpus, related with health topics, but showing a significant variety in terms of format and structure.
Furthermore, the majority of sentences are in Spanish, but a small set of English sentences is also included, to evaluate generalisation across domains.

@@

As in previous edition, the corpus for eHealth-KD 2021 is based mostly on text extracted from \textit{Medline} sources, plus additional resources.
First, the same corpus used in the 2020 edition will be provided for training and development, while a new set of previously unlabelled sentences will be manually annotated and used for the test collection. Additionally, health-related news sourced from \textit{Wikinews} will be also provided for training and development.
Finally, a small set of sentences from scientific papers in the \textit{CORD-19} corpus (in English language) are selected, annotated, and distributed in the development, and testing collections. Overall, the composition of the corpus is presented in Table~\ref{tab:corpus}\footnote{\url{https://ehealthkd.github.io/2021/resources}}.

@@

@@

\todo[inline]{Comentar GuanZengyi con respecto a la complejidad del transfer learning...}

\begin{table*}[htb]
  \resizebox{\textwidth}{!}{
  \begin{tabular}{l|rrrr|rrrr|rrrr}
    \toprule
    & \multicolumn{4}{c|}{\textit{Medline}} & \multicolumn{4}{c|}{\textit{Wikinews}} & \multicolumn{4}{c}{\textit{CORD}} \\
    & \multicolumn{2}{c}{\textbf{Task A}} & \multicolumn{2}{c|}{\textbf{Task B}} & \multicolumn{2}{c}{\textbf{Task A}} & \multicolumn{2}{c|}{\textbf{Task B}} & \multicolumn{2}{c}{\textbf{Task A}} & \multicolumn{2}{c}{\textbf{Task B}} \\
    \textbf{Team} & $F_1$ & \textit{Diff} & $F_1$ & \textit{Diff} & $F_1$ & \textit{Diff} & $F_1$ & \textit{Diff} & $F_1$ & \textit{Diff} & $F_1$ & \textit{Diff} \\
    \midrule
Vicomtech        & \bf 0.843 &  0.156 & 0.467 & 0.093 & \bf 0.794 & 0.106 & 0.478 &  0.104 & 0.576 & -0.111 & 0.256 & -0.118 \\
PUCRJ-PUCPR-UFMG & 0.779 &  0.071 & 0.374 & 0.109 & 0.781 & 0.073 & 0.362 &  0.098 & \bf 0.641 & -0.067 & 0.170 & -0.095 \\
IXA              & 0.699 &  0.045 & \bf 0.562 & 0.130 & 0.714 & 0.060 & \bf 0.493 &  0.062 & 0.609 & -0.045 & \bf 0.338 & -0.094 \\
uhKD4            & 0.772 &  0.242 & 0.538 & 0.219 & 0.714 & 0.184 & 0.431 &  0.112 & 0.348 & -0.182 & 0.127 & -0.192 \\
UH-MMM           & 0.692 &  0.081 & 0.158 & 0.104 & 0.695 & 0.083 & 0.061 &  0.006 & 0.538 & -0.073 & 0.014 & -0.041 \\
Codestrange      & 0.177 &  0.096 & 0.138 & 0.105 & 0.124 & 0.042 & 0.008 & -0.025 & 0.017 & -0.065 & 0.000 & -0.033 \\
JAD              & 0.238 & -0.025 & 0.036 & 0.028 & 0.243 & -0.02 & 0.000 & -0.007 & 0.280 &  0.017 & 0.000 & -0.007 \\
GuanZhengyi      & 0.807 &  0.470 & 0.000 & 0.000 & 0.286 & -0.05 & 0.000 &  0.000 & 0.000 & -0.336 & 0.000 &  0.000 \\
Maoqin           & 0.266 &  0.094 & 0.000 & 0.000 & 0.269 & 0.097 & 0.000 &  0.000 & 0.000 & -0.172 & 0.000 &  0.000 \\
    \midrule
    Mean difference &       & 0.136 &       & 0.087 &       & 0.063 &       & 0.038 &       & -0.114 &       & -0.064 \\
    \bottomrule
  \end{tabular}}
  \caption{Individual results per domain in subtasks A and B. The \textit{Diff} column corresponds to the absolute difference between the presented $F_1$ and the aggregated $F_1$ on the corresponding scenario,
  as reported in Table~\ref{tab:results}. A positive \textit{Diff} indicates that team had a correspondingly better result on that specific subset than in the overall corpus.\label{tab:models}}
\end{table*}

\todo[inline]{Grafica de lineas para ver la evolucion del transferlearning entre diminios}

@@

Moving towards a full solution to the eHealth-KD challenge, there are some fundamental obstacles that still need to be tackled.
The most salient one is effectively capturing the interaction between entities and the semantic relations in which they appear.
As we have learned from observing human annotators, they usually annotate simultaneously entities and relations.
Furthermore, they do not follow the left-to-right natural order of the sentence, but rather annotate the most salient entities first~(e.g., the main Action and related Concepts) and then add the contextual relations and supporting entities.
Although it is unclear whether this strategy is necessary, it presents an interesting alternative approach for designing an automatic annotation system in the form of an agent that performs annotation actions on the sentence, perhaps trained with a reinforcement learning approach.
For this purpose, it could be interesting to analyse not only the final annotated sentence but the individual annotation events that human annotators produce, including the undoing previous annotations.

@@

\section*{Acknowledgements}
This research has been supported by a Carolina Foundation grant in agreement with University of Alicante and University of Havana. Moreover, the research has been partially funded by the University of Alicante and the University of Havana, the Generalitat Valenciana (\textit{Conselleria d’Educació, Investigació, Cultura i Esport}) and the Spanish Government through the projects LIVING-LANG (RTI2018-094653-B-C22), INTEGER (RTI2018-094649-B-I00)  and SIIA (PROMETEO/2018/089, PROMETEU/2018/089). Additionally, it has been backed by the work of both COST Actions: \texttt{CA19134} -- \textit{``Distributed Knowledge Graphs''} and \texttt{CA19142} -- \textit{``Leading Platform for European Citizens, Industries, Academia and Policymakers in Media Accessibility''}.

>>>>

\documentclass[a4paper,11pt,twocolumn,twoside]{article}
\usepackage{graphicx}
\usepackage{sepln_en}
\usepackage{fullname}
\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{todonotes}
\usepackage{url}

% \usepackage[spanish,es-nosectiondot, es-tabla, es-noindentfirst, es-nolists]{babel}

@@

\seplnabstract{This paper summarises the eHealth Knowledge Discovery Challenge hosted at IberLEF 2021. We describe the task, resources, and participating systems, highlighting and discussing the main results achieved in the challenge. We analyse the best performing systems and present recommendations for future research.}

@@

The Challenge is based on a corpus of documents composed of
sentences taken from previous challenges and other resources,
and newly annotated sentences.
The corpus is divided into three collections: training, development, and testing.
All collections contain sentences extracted from MedlinePlus, Wikinews, and the CORD-19 corpus, related with health topics, but showing a significant variety in terms of format and structure.
Furthermore, the majority of sentences are in Spanish, but a small set of English sentences is also included, to evaluate generalisation across domains.
The corpus with both annotated files in ANN format and ready-to-use files for training and evaluation is available online\footnote{\url{https://github.com/ehealthkd/corpora}}.

@@

As in previous edition, the corpus for eHealth-KD 2021 is based mostly on text extracted from \textit{Medline} sources, plus additional resources.
First, the same corpus used in the 2020 edition will be provided for training and development, while a new set of previously unlabelled sentences will be manually annotated and used for the test collection. Additionally, health-related news sourced from \textit{Wikinews} will be also provided for training and development.
Finally, a small set of sentences from scientific papers in the \textit{CORD-19} corpus (in English language) are selected, annotated, and distributed in the development, and testing collections. Overall, the composition of the corpus is presented in Table~\ref{tab:corpus}.

@@

\begin{table*}[htb]
  \resizebox{\textwidth}{!}{
    \begin{tabular}{l|rrrr|rrrr|rrrr}
      \toprule
                       & \multicolumn{4}{c|}{\textit{Medline}} & \multicolumn{4}{c|}{\textit{Wikinews}} & \multicolumn{4}{c}{\textit{CORD}}                                                                                                                                                                                                          \\
                       & \multicolumn{2}{c}{\textbf{Task A}}   & \multicolumn{2}{c|}{\textbf{Task B}}   & \multicolumn{2}{c}{\textbf{Task A}} & \multicolumn{2}{c|}{\textbf{Task B}} & \multicolumn{2}{c}{\textbf{Task A}} & \multicolumn{2}{c}{\textbf{Task B}}                                                                                     \\
      \textbf{Team}    & $F_1$                                 & \textit{Diff}                          & $F_1$                               & \textit{Diff}                        & $F_1$                               & \textit{Diff}                       & $F_1$     & \textit{Diff} & $F_1$     & \textit{Diff} & $F_1$     & \textit{Diff} \\
      \midrule
      Vicomtech        & \bf 0.843                             & 0.156                                  & 0.467                               & 0.093                                & \bf 0.794                           & 0.106                               & 0.478     & 0.104         & 0.576     & -0.111        & 0.256     & -0.118        \\
      PUCRJ-PUCPR-UFMG & 0.779                                 & 0.071                                  & 0.374                               & 0.109                                & 0.781                               & 0.073                               & 0.362     & 0.098         & \bf 0.641 & -0.067        & 0.170     & -0.095        \\
      IXA              & 0.699                                 & 0.045                                  & \bf 0.562                           & 0.130                                & 0.714                               & 0.060                               & \bf 0.493 & 0.062         & 0.609     & -0.045        & \bf 0.338 & -0.094        \\
      uhKD4            & 0.772                                 & 0.242                                  & 0.538                               & 0.219                                & 0.714                               & 0.184                               & 0.431     & 0.112         & 0.348     & -0.182        & 0.127     & -0.192        \\
      UH-MMM           & 0.692                                 & 0.081                                  & 0.158                               & 0.104                                & 0.695                               & 0.083                               & 0.061     & 0.006         & 0.538     & -0.073        & 0.014     & -0.041        \\
      Codestrange      & 0.177                                 & 0.096                                  & 0.138                               & 0.105                                & 0.124                               & 0.042                               & 0.008     & -0.025        & 0.017     & -0.065        & 0.000     & -0.033        \\
      JAD              & 0.238                                 & -0.025                                 & 0.036                               & 0.028                                & 0.243                               & -0.02                               & 0.000     & -0.007        & 0.280     & 0.017         & 0.000     & -0.007        \\
      GuanZhengyi      & 0.807                                 & 0.470                                  & 0.000                               & 0.000                                & 0.286                               & -0.05                               & 0.000     & 0.000         & 0.000     & -0.336        & 0.000     & 0.000         \\
      Maoqin           & 0.266                                 & 0.094                                  & 0.000                               & 0.000                                & 0.269                               & 0.097                               & 0.000     & 0.000         & 0.000     & -0.172        & 0.000     & 0.000         \\
      \midrule
      Mean difference  &                                       & 0.136                                  &                                     & 0.087                                &                                     & 0.063                               &           & 0.038         &           & -0.114        &           & -0.064        \\
      \bottomrule
    \end{tabular}}
  \caption{Individual results per domain in subtasks A and B. The \textit{Diff} column corresponds to the absolute difference between the presented $F_1$ and the aggregated $F_1$ on the corresponding scenario,
    as reported in Table~\ref{tab:results}. A positive \textit{Diff} indicates that team had a correspondingly better result on that specific subset than in the overall corpus.\label{tab:models}}
\end{table*}

@@

Figure~\ref{fig:transfer} represents the performance for each team across different subset collections of the testing set. As it can be observed, most teams present a significant drop in performance, in both subtasks, for the CORD subset with respect to the Medline and the Wikinews subsets.
This highlights the relative difficulty of the transfer learning component of the challenge.
IXA presented the most robust system in this respect.
As an illustrative example, the system presented by GuanZengyi obtained the second best results on the Medline subset of the testing collection, but their performance drops sharply in the remaining subsets, hence achieving an overall score marginally superior to the baseline.

\begin{figure*}
  \includegraphics[width=\textwidth]{transfer.png}
  \caption{Graphical representation of the performance by team in each subset collection of the testing set. Each bar represents the scores obtained by each team in both subtasks in a specific subset collection.\label{fig:transfer}}
\end{figure*}

@@

Moving towards a full solution for the eHealth-KD challenge, there are some fundamental obstacles that still need to be tackled.
The most salient one is effectively capturing the interaction between entities and the semantic relations in which they appear.
As we have learned from observing human annotators, they usually annotate entities and relations simultaneously.
Furthermore, they do not follow the left-to-right natural order of the sentence, but rather annotate the most salient entities first~(e.g., the main Action and related Concepts) and then add the contextual relations and supporting entities.
Although it is unclear whether this strategy is necessary, it presents an interesting alternative approach for designing an automatic annotation system in the form of an agent that performs annotation actions on the sentence, perhaps trained with a reinforcement learning approach.
For this purpose, it could be interesting to analyse not only the final annotated sentence but the individual annotation events that human annotators produce, including the undoing previous annotations.

@@

\section*{Acknowledgements}
This research has been supported by a Carolina Foundation grant in agreement with University of Alicante and University of Havana. Moreover, the research has been partially funded by the University of Alicante and the University of Havana, the Generalitat Valenciana (\textit{Conselleria d’Educació, Investigació, Cultura i Esport}) and the Spanish Government through the projects LIVING-LANG (\texttt{RTI2018-094653-B-C22}), INTEGER (\texttt{RTI2018-094649-B-I00})  and SIIA (\texttt{PROMETEO/2018/089}, \texttt{PROMETEU/2018/089}). Additionally, it has been backed by the work of both COST Actions: \texttt{CA19134} -- \textit{``Distributed Knowledge Graphs''} and \texttt{CA19142} -- \textit{``Leading Platform for European Citizens, Industries, Academia and Policymakers in Media Accessibility''}.
